---
output: github_document
---

# pkginspectr

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

`pkginspectr` lets you peek inside R packages. It inspects local folders as well as packages downloaded from GitHub or CRAN and returns tidy tibbles that are easy to work with.

Key functions include:

-   `inspect_package()` – summarises file structure, function files, tests and docs.
-   `get_code_stats()` – counts lines of code, comments and tests.
-   `plot_pkginspect()` – draws simple but customisable bar charts of the results in the console.

## Installation

You can install the development version from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("ddauber/pkginspectr")
```

## Inspect a package

Want a quick overview of what’s inside an R package?
`pkginspectr` lets you count files, functions, and other components in seconds.

```{r inspect-package}
library(pkginspectr)

inspect_package("ddauber/pkginspectr")
```

## Compute code statistics

Go beyond file counts and see how much code is really there.
`get_code_stats()` analyses line counts across the package.

```{r get-code-stats}
get_code_stats("ddauber/pkginspectr")
```

## Visualise in the console

No need for heavy graphics — `plot_pkg()` renders Unicode bar charts right in your terminal.

```{r plot-pkginspect}
inspect_package("ddauber/pkginspectr") |>
  plot_pkg()
```

You can customise the look to meet your needs: bars are just glyphs and ANSI colours, so you can tweak:
- colours (e.g. `text_col`, `bar_col`, etc.),
- bar shape (`glyph`, `start`, `end`),
- scale/fit (`max_bars`), or
- add a custom title (`title`)

## Inspect multiple packages at once

Compare packages side by side — perfect for exploring codebases or teaching.

```{r inspect-multiple}
inspect_package(c(
  "ddauber/pkginspectr",
  "ddauber/tidycomp",
  "ddauber/r4np"
)) |>
  plot_pkg(type = "metric")
```

Here `type = "metric"` switches from a per‑package breakdown to a metric‑centric view
(e.g., compare `num_r_files`, `num_test_files`, `docs`, etc. across packages).

This package is meant to be a small and fun package with some useful functionality. Enjoy exploring your own R packages (as much as others’ packages)!